---
title: "PS2-feedback"
format: html
editor: visual
---

## PS 2 Feedback
I'd like to see more commentary on your .qmd file. For example, after you examine the data with `str()` and `glimpse()` I'd like to know what you learned by doing so. You might write "My data consist of 49 rows and 7 variables. Two variables should probabaly be factor, one character and the rest numeric" or something. You might also note any observations you make just by looking at the data.

On line 37,  you indicate that you are going to make `costume` into a factor. You didn't end up doing that (which was the correct choice) but you should make sure your commentary matches your code.

Think of the `.qmd` as the record - if you came back to this project in a year, and only had the `.qmd` and not the assignment handout, would you know what is going on?

I'm glad that on line 66 you re-ran `levels()` to make sure that your fix worked!

You didn't do any error checking on the numeric variables.

A suggestion for your code. Use spacing to help improve readability. YOu are doing pretty well at this, but in this example from your lines 117 - 123 you have:

```{r}
halloween |>
  group_by(sugar_high) |>
  summarize(mean_age = mean(age), sd_age = sd(age),
            mean_grams = mean(g_candy_consumed), sd_grams = sd(g_candy_consumed)) |>
  View()
```

And if you break up that `summarise()` a bit more like this:

```{r}
halloween |>
  group_by(sugar_high) |>
  summarize(
    mean_age = mean(age), 
    sd_age = sd(age),
    mean_grams = mean(g_candy_consumed), 
    sd_grams = sd(g_candy_consumed)) |>
  View()
```
 
The code is exactly the same but it is easier to read in the second version.

Overall though, nice job!